My title

### 2024-02-08 paper/paper.qmd
deleting library i didnt need

library(tidyverse)
library(palmerpenguins)
```

@@

tibble(year = 1875:1972,
       level = as.numeric(datasets::LakeHuron)) |>
  ggplot(aes(x = year, y = level)) +
  labs(x = "Year", 
       y = "Height (ft)")
  geom_point()
```

>>>>

library(tidyverse)
library(palmerpenguins)
install.packages(tinytex)
library(tinytex)
```

@@

tibble(year = 1875:1972,
       level = as.numeric(datasets::LakeHuron)) |>
  ggplot(aes(x = year, y = level)) +
  labs(x = "Year", 
       y = "Height (ft)") +
  geom_point() +
  theme_bw()
```
